### 2024-07-18 conteudo/methods/methods.tex
Fix grammar errors with grammarly free tier

To answer our proposed research questions, we opted to divide our research. Firstly, we will approach the supplementary research 
RQ1.1, which will serve as a background to our research question RQ1. To answer the RQ1.1, we propose a multiple-method investigation,
by validating our proposed tool in the BigCloneBench databaset \citep{bigclonebench}, which is the standard method used by the
literature, and a empirical analyses of a selected subset of functions in which the tool infers.
With the question RQ1.1 answered, we will return our focus to the RQ1. To answer the RQ1, we opted to create a ethnographic study, 
using participant-observation methodology, we expect to mitigate a selected subset of duplicated functions by refactoring them using
a designed sistematic approach, while iteracting with the Linux community to collect feedback of the mitigation made by us.

@@

The multiple-method investigation to verify the efficiency of our tool in a methodical way is a method in which we consider 
trustworthy.
The first method used is the evaluation of the proposed tool in the BigCloneBench database \citep{bigclonebench}, one of the 
standard code duplication databases used by validation of tool presented in the formal literature. 
As presented by Krinke and Ragkhitwetsagul, the BigCloneBench is not a perfect dataset \citep{bigfail}, and for that reason we opted to do
a additional evalution, in which we will do a empirical analyses on a select subset of functions of the AMD Display driver in which
our tool infers it is a duplication. To a concrete evaluatiion, in both of the methods we will apply a  variation of the similarity 
metric (The similarity metric is a metric measuring the similarity of two code duplications, a proper explanation is made 
in the Chapter \ref{cha:tool}).

@@

The BigCloneBench dataset \citep{bigclonebench} is a collection of Java code with a selection of code duplications pairs categorized by the authors, these
code duplications pairs are not separed solely if they are duplications, the pairs are also categorized by the code duplication
types presented in Subsection \ref{subsec:types}.

Liut et al presented a sample method to evaluate the their code duplications detection method, in which they sample 20,000 pairs
from each of the code duplication types, with the addition of 20,000 nonduplication pairs to act as the negative samples
\citep{tailor}. To a fairness evaluation, we use the same sample method as them to evaluate our tool.

The proposed tool does not differentiate the code duplication types and infers duplications in the function level instead of the 
code file level, which is the standard in the state-of-art code duplication methods, we were required to adjust the form 
we compute metrics of the evalution. To accomplish this, we will define that every pair of functions in which the similarity metric
is equal or superior to a threshold X will be considered a duplication, and the pair of code files that the functions are contained
are marked as duplication. If on this method, a code duplication pair is corretly indentified, it will count as a correct to its 
code duplication types, if a incorrect duplication pair is infered, it will count as incorrect to all code duplication types. Given
these definitions, we will compute the Recall metric presented in \ref{subsec:codemethods} for each of the code duplication types.

To understand the variation of meaning when we change the similarity threshold, we will eval our tool for the given variations of
the threshold X and discuss the results: 30\%, 40\%, 50\%, 60\%, 70\%, 80\%, 90\%, 100\%.

@@

Given the problems of the BigCLoneBench presented by Krinke and Ragkhitwetsagul \citep{bigfail} and the limitations of it in our
scope such as being a Java dataset while the Linux kernel are primarily build in the C programming language, we opted to, together
with the formal litarature evaluation, perform a empirical study analyzing the codes in which our tool infered as duplications.

The number of code lines and components in the Linux kernel makes it impractical to analyse every code duplication. To limit our
scope, we will analyse solely code duplications in the AMD Display driver. This limitation is still does not reduce the code
duplication to analyse, since in our preliminar tool execution showed in the Figure \ref{fig:relatory_ex}, there is over 20,000
lines of code duplications on the AMD Display driver with similarity metric of 100\%.

For conducting our empiricial analyses, we opted to do a random selection in the code duplications pairs infered by our tool. To
do that, we will use the definition that if the similarity metric of a function pair is greater or equal to X, will be considered a
duplication. To understand the optimal values of X we will analyse 10 functions pair randomic selected 
that have similarity metric X for each of the variations of the parameter X, which are 
30\%, 40\%, 50\%, 60\%, 70\%, 80\%, 90\%, 100\%. 
As it is not expected to have code duplications with similarity exactly a whole number, we will allow a
variation of 1\% for greater or less to each of the variations of the parameter X.

To do the random selection of functions pairs, we list the code duplications for each of the variations of X and execute 
a random selection algorithm
builtin in in the source code language of our tool. The exactly algorithm of the random selection, along with the selected 
function pairs can be found in Appendix (CREATE APENDICE AND ADD HERE).

When we analyses the selected functions pairs, we will judged empiricaly if they are a duplication or not, then we are not
going further as
categorizing the duplications by code duplication type. We intend to collect the data on this empirical analyses and compare it
to the formal literature method, to undertand if our tool in fact detect duplicated functions and 
the difference it makes when varying the minimum similarity parameter of our tool.

@@

Ethnography is a research method recognized as a significant qualitative empirical approach 
suited to understanding people and cultures, and their associated social and work practices \citep{bookethno}. 
The central tenet of the ethnography approach is to enable research to undertand values, beliefs or ideas shared for a 
 community under study from the members' point of view \citep{ethnosoft}. Thus, the ethnographer is required to act as
a member of  the community, learning and observing deeply what people do and why they do.

Sharp et al discuss the application of the ethnography method in the software engineering research, demonstrating the low adoption 
of the method and its advantages to uncover what practioners do and why they do \citep{ethnosoft}. In our research context, if we
mitigate code duplications by ourselves without iteracting with the Linux community, we cannot undertand if the linux maintainers 
would accept our approach for code duplication and what concerns they would have. Thus, we resorted to a ethnography research, where
we will act as a member of the Linux kernel, begin a contributor with focus on removing code duplications found.

On this section, we will describe a generic approach pipeline to mitigate code duplication found in the Linux kernel. Then we
will describe the methodology to select a subset of duplicated functions found by our tool and finally, describe the ethnographic
methodology to interact with the Linux community.

\subsection{Generic approach pipeline to mitigate code duplication}

@@

The C programming language's way to communicate between source code files is through creation of header files, which is
a library specification \citep{Cbook}. As the Linux kernel is mainly build in C, we resorted to remove code duplications by
creating a library, where the code artifacts, instead of using their duplications, will pass to use the library.

When removing duplicated functions, our desired behavior is to this function to every portion of the code it exist, only allowed a
unique version existent in the library created by us. For this reason, given our initial duplicated function pair, we will use 
the function information functionality(This functionality is described in \ref{subsec:functioncommand}) of our tool to find all 
places that this function is defined in the source code. Thus, we finish with a collection of duplicated function and the collection
of code files in which these functions are defined into.

Given the semantics of a library to containing the shared code by a collection of code files, we added a additional step of the 
approach, which is searching for others functions contained in all of code files of the collection we are working with. 
On this moment, we have a collection of code files, and a non-empty set of functions which are shared by all of the code files 
in the collection.

Finally, for each of the functions shared by all code files, we do a specific-case aproach to mitigate each one of them.
If a function is shared perfectly by all the code files, we use a simply approach to only remove them and create the function in
the source code file, if it is not shared perfectly, we look for refactoring methods which can be applied on this specific case.

Finishing our mitigation method, if the mitigation ended up working in a initial step, we move it foward to the 
Ethnographic method, iteracting with the Linux community to understand what are their thoughts on the mitigation. If the mitigation
ended up as not working as expected, we will categorized it in two categories, the first one is that the refactoring requires a
decision in which we, as not specialist and non-maintainers of the Linux kernel, cannot make it correctly, although
we believe a specialist would be able to refactoring it. The second categorization is that we do not know if it is in fact possible
to refactoring the duplication.

The figure (CREATE FIGURE AND ADD HERE) ilustrates the approach pipeline described in this section.

@@

As discussed in the empyrical analyses for the tool, it is impractical to evaluate every code duplication on Linux kernel. Thus,
similarily to the empyrical analyses for the tool, we will limit the experiment scope to only the AMD Display driver and select
a random sample of duplicated functions infered by our tool to initiate the mitigation approach defined in \ref{subsec:pipeline}. 
We chose a sample size of 30 duplicated functions, as there are multiples studies demonstrated that a sample size of this size 
have a statistical significance \citep{sample1,sample2}.

On the the random selection of the duplicated functions, we deside to put a additional restriction on which functions pairs are 
elegible to be selected. The restriction is that we will only select functions pairs with similarity metric equal 
to 100\%, we made this choice because, as showed in the Figure \ref{fig:relatory_ex}, there are more then 20,000 lines codes 
in the AMD Display driver in which the similarity metric reaches this value. On all function pairs that respect the restriction,
we will choose then uniformly at random.

The functions pairs selected at random following our methodoly can be consulted in the Table (CREATE TABLE AND ADD HERE).

@@

>>>>

To answer our proposed research questions, we opted to divide our research. Firstly, we will approach 
the supplementary research RQ1.1, which will serve as a background to our research question RQ1. 
To answer the RQ1.1, we propose a multiple-method investigation by validating our proposed tool in 
the BigCloneBench dataset \citep{bigclonebench}, which is the standard method used by the literature, 
and an empirical analysis of a selected subset of functions in which the tool infers. With the question 
RQ1.1 answered, we will return our focus to the RQ1. To answer the RQ1, we opted to create an 
ethnographic study using participant-observation methodology. We expect to mitigate a selected subset 
of duplicated functions by refactoring them using a designed systematic approach while interacting 
with the Linux community to collect feedback on the mitigation made by us.

@@

The multiple-method investigation to verify the efficiency of our tool is a method that we 
consider trustworthy. The first method used is to evaluate the proposed tool in the BigCloneBench 
database \citep{bigclonebench} one of the standard code duplication databases used to validate 
the tool presented in the formal literature. As presented by Krinke and Ragkhitwetsagul, the 
BigCloneBench is not a perfect dataset \citep{bigfail}. For that reason, we opted 
to do an additional evaluation, in which we will do an empirical analysis on a select subset of 
functions of the AMD Display driver, which our tool infers is a duplication. For a concrete evaluation,
in both methods, we will apply a variation of the similarity metric (The similarity metric is a 
metric that measures the similarity of two code duplications; a proper explanation is made
in Chapter \ref{cha:tool}).

@@

The BigCloneBench dataset \citep{bigclonebench} is a collection of Java code with a selection of
code duplication pairs categorized by the authors. These code duplication pairs are labeled by 
the code clone type described in \ref{subsec:types}.

Liut et al. presented a sample method to evaluate their code duplication detection method, 
in which they sample 20,000 pairs from each of the code duplication types with the addition 
of 20,000 nonduplication pairs to act as the negative samples \citep{tailor}. 
For a fair evaluation, we use the same sample method as them to evaluate our tool.

The proposed tool does not differentiate the code duplication types and infers duplications 
at the function level instead of the code file level, which is the standard in state-of-the-art 
methods. We were required to adjust the form we computed metrics of the evaluation. To accomplish 
this, we will define that every pair of functions in which the similarity metric is equal or 
superior to a threshold X will be considered a duplication, and the pair of code files in which 
the functions exist are labeled as duplication. If, on this method, a code duplication pair is 
correctly identified, it will count as correct to its code duplication types. If an incorrect 
duplication pair is inferred as a duplication, it will count as incorrect to all code duplication 
types. Given these definitions, we will compute the Recall metric presented in \ref{subsec:codemethods}
for each code duplication type.

To understand the variation of meaning when we change the similarity threshold, we will evaluate 
our tool for the given variations of the threshold X and discuss the results: 
30\%, 40\%, 50\%, 60\%, 70\%, 80\%, 90\%, 100\%.

@@

Given the problems of the BigCLoneBench presented by Krinke and Ragkhitwetsagul \citep{bigfail}
and the limitations of it in our scope, such as being a Java dataset while the Linux kernel 
is predominantly built in the C programming language, we opted to, together with the formal 
literature evaluation, perform an empirical study analyzing the codes in which our tool inferred 
as duplications.

The number of code lines and components in the Linux kernel makes it impractical to analyze every 
code duplication. To limit our scope, we will analyze solely code duplications in the AMD Display 
driver. This limitation still does not reduce the code duplication to analyze. In our preliminary 
tool execution shown in Figure \ref{fig:relatory_ex}, there are over 20,000 lines of code 
duplications on the AMD Display driver with a similarity metric of 100\%.

For our empirical analyses, we opted to make a random selection in the code duplication pairs 
inferred by our tool. To do that, we will use the definition that if the similarity metric of a 
function pair is greater or equal to X is considered a duplication. To understand the optimal 
values of X, we will analyze 10 functions pair random selected that have similarity metric X 
for each of the variations of the parameter X, which are 
30\%, 40\%, 50\%, 60\%, 70\%, 80\%, 90\%, 100\%. 
As it is unexpected to have code duplications with similarity equals a whole number, we will 
allow a variation of 1\% for greater or less to each of the variations of the parameter X.

To make the random selection of function pairs, we list the code duplications for each of the 
X variations and execute a random selection algorithm built into the source code language of 
our tool. The exact algorithm of the random selection, with the selected function pairs, can 
be found in the Appendix (CREATE Appendix AND ADD HERE).

When we analyze the selected function pairs, we will empirically judge if they are duplications,
which means we are not going deeper as categorizing the duplications by code duplication type. 
We intend to collect the data on this empirical analysis and compare it to the formal literature 
method to understand if our tool detects duplicated functions and the difference it makes when 
varying the minimum similarity parameter of our tool.

@@

Ethnography is a research method recognized as a significant qualitative empirical approach to 
understanding people, their cultures, and their associated social and work practices \citep{bookethno}.
The central tenet of the ethnography approach is to enable researchers to understand values, 
beliefs, or ideas shared by a community under study from the members’ point of view 
\citep{ethnosoft}. Thus, the ethnographer acts as a community member, learning and observing 
what people do and why they do it.

Sharp et al. discuss the application of the ethnography method in software engineering research, 
demonstrating the low adoption of the method and its advantages in uncovering what practitioners 
do and why they do it \citep{ethnosoft}. In our research context, if we mitigate code 
duplications by ourselves without interacting with the Linux community, we cannot understand if 
the Linux maintainers would accept our approach for code duplication and what concerns they 
would have. Thus, we resorted to ethnography research, where we will act as a member of the 
Linux kernel and act as a contributor with a focus on removing code duplications found.

In this section, we will outline a systematic approach to mitigate code duplication in the 
Linux kernel. Next, we will detail the methodology for selecting a subset of duplicated functions 
identified by our tool. Finally, we will describe the ethnographic methodology for interacting 
with the Linux community.

\subsection{Systematic approach to mitigate code duplication}

@@

The C programming language’s way to communicate between source code files is through creating 
header files, which is a library specification \citep{Cbook}. As the Linux kernel 
is predominantly built in C, we remove code duplications by creating a library where the code 
artifacts will use the library instead of their duplications.

When removing duplicated functions, our desired behavior is to remove the functions in every 
portion of the code in which the functions exist, only allowing a unique version to exist in 
the library created. For this reason, given our initial duplicated function pair, we will use 
the function information functionality(Described in \ref{subsec:functioncommand}) to find all
places where this function exists in the source code. Thus, we finish with a collection of 
duplicated functions and the code files in which these functions exist.

Given the semantics of a library containing the shared code by a collection of code files, 
we added a step of the approach, which is searching for other functions contained in all of 
the code files of the collection we are working with. Thus, we have a collection of code files 
and a non-empty set of functions shared by all the code files in the collection.

Finally, for each of the functions shared by all code files, we make a specific-case approach 
to mitigate each one of them. If a function is shared by all the code files without 
modifications, we use a simple approach to only remove them and create the function in the 
source code file. If it is shared with modifications, we look for refactoring methods applicable 
to this specific case.

Finishing our mitigation method, if the mitigation ends up working in an initial step, we may 
move it forward to the Ethnographic method, interacting with the Linux community to understand 
their thoughts on the mitigation. If the mitigation ends up not working as expected, we will 
categorize it in two categories, the first one is that the refactoring requires a decision in 
which we, as not specialists and non-maintainers of the Linux kernel, cannot make it correctly,
although we believe a specialist would be able to refactor it. The second categorization is 
that we do not know if it is possible to refactor the duplication. With or without successful 
mitigation, we will store our mitigations on (ADD REP AND PUT HERE) to research transparency.

The figure (CREATE FIGURE AND ADD HERE) illustrates the systematic approach described in this section.

@@

As discussed in the empirical analyses for the tool, it is impractical to evaluate every code 
duplication on the Linux kernel. Thus, similarly to the empirical analyses for the tool, we will 
limit the experiment scope to only the AMD Display driver and select a random sample of duplicated 
functions inferred by our tool to initiate the mitigation approach defined in \ref{subsec:pipeline}. 
We chose a sample size of 30 duplicated functions, as multiple studies demonstrated that a sample 
size of this size has statistical significance \citep{sample1,sample2}.

On the random selection of the duplicated functions, we decided to put an additional restriction 
on which function pairs are eligible to be selected. The restriction is that we will choose function 
pairs with a similarity metric equal to 100\%. We made this choice because, as shown in \ref{fig:relatory_ex},
there are more than 20,000 lines of code in the AMD Display driver in which the similarity metric 
reaches this value. On all function pairs that respect the restriction, we will choose them 
uniformly at random.

(MAYBE I SHOULD ADD A RESTRICTION ABOUT IGNORING AUTOMATED GENERATED CODE, such as DML folder)

The function pairs selected randomly following our methodology can be consulted in the Table
(CREATE TABLE AND ADD HERE).

@@

When we make a code duplication mitigation following our systematic approach described in 
\ref{subsec:pipeline}, we are apt to initiate our ethnographic research. We resorted to a
participant-observation approach as our ethnographic methodology, where we will act as 
contributors of the Linux kernel to the AMD Display driver, interacting with the maintainers 
of the AMD Display driver attempting to get our mitigations added to the Linux kernel.

The Linux kernel communication is made through public mailing lists, where anyone can consult 
the discussions. We plan to collect data artifacts through the AMD Display driver mailing list. 
The mailing list will register our interactions with the Linux community, with their members 
sharing their opinions and suggestions for the mitigation we made, corroborating the discussion 
about the effectiveness of our proposed approach.

Given the time limit of our research, we do not expect to be able to interact with the Linux 
community throughout the successful mitigation we made using the proposed approach, as it passes 
through factors we do not control, which is the time spent waiting for Linux community’s members 
interact with us. For this reason, we resorted to committing to do the participant-observation 
approach in 5 of the successful mitigations and use them for our discussion.
